---
title: "CytoMethIC models"
date: "`r BiocStyle::doc_date()`"
package: askme
output: BiocStyle::html_document
fig_width: 6
fig_height: 5
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{"1. models"}
  %\VignetteEncoding{UTF-8}
---

```{r message=FALSE, warning=FALSE}
library(sesame)
library(CytoMethIC)
library(dplyr)
```

```{r}
model_home = "https://github.com/zhou-lab/CytoMethIC_models/raw/main/models"
cmi_checkVersion()
```

The mature CytoMethIC models are hosted in ExperimentHub. This package also
supports using models from https://github.com/zhou-lab/CytoMethIC_models, which
will host the most frequently updated public repository of our lab's classifiers.

```{r cyto3, result="asis", echo=FALSE}
library(knitr)
kable(cmi_models[, c("EHID", "PredictionLabelDescription", "Title")],
    caption = "CytoMethIC supported models"
)
```

# Gender

The gender/sex model is based on X chromosome inactivation sites, including both hyper
and hypomethylation on inactive X.

```{r model_sex, message=TRUE}
betas_hm450 = sesameDataGet("HM450.1.TCGA.PAAD")$betas
cmi_model = readRDS(url(paste0(model_home, "/Sex2_HM450.rds")))
cmi_predict(betas_hm450, cmi_model)
kable(table(cmi_model$stats$additional_info, cmi_model$stats$truth))
```

# Ethnicity

The below snippet shows a demonstration of the cmi_classify function working to
predict the ethnicity of the patient.

```{r model_ethnicity1, message=FALSE}
betas_hm450 = sesameDataGet("HM450.1.TCGA.PAAD")$betas
cmi_model = ExperimentHub()[["EH8421"]]
cmi_predict(betas_hm450, cmi_model)
```

```{r model_ethnicity2}
betas_epicv2 = openSesame(sesameDataGet("EPICv2.8.SigDF")[[1]])
cmi_model = readRDS(url(paste0(model_home, "/Race3_rfcTCGA_InfHum3.rds")))
cmi_predict(betas_epicv2, cmi_model, lift_over=TRUE)
```

# Mitotic Index

```{r replitali}
cmi_model = readRDS(url(paste0(model_home, "/RepliTali_EPIC.rds")))
betas_hm450 = sesameDataGet("HM450.1.TCGA.PAAD")$betas
cmi_predict(betas_hm450, cmi_model)


cmi_model = readRDS(url(paste0(model_home, "/TumorPurity_HM450.rds")))
betas_hm450 = sesameDataGet("HM450.1.TCGA.PAAD")$betas
cmi_predict(betas_hm450, cmi_model)


```

# Cancer Classification Models

## CNS Cancer

```{r message=FALSE}
betas_hm450 = sesameDataGet("HM450.1.TCGA.PAAD")$betas
cmi_model = ExperimentHub()[["EH8396"]]
## cmi_model = readRDS(url(paste0(model_home, "/CancerType33_rfcTCGA_InfHum3.rds")))
cmi_predict(betas_hm450, cmi_model, lift_over=TRUE)
```

# Cancer Phenotyping Models

## Cancer Cell of origin

The below snippet shows a demonstration of the cmi_classify function working to
predict the cell of origin of the cancer.

```{r cyto7, message=FALSE}
betas_hm450 = sesameDataGet("HM450.1.TCGA.PAAD")$betas
cmi_model = ExperimentHub()[["EH8423"]]
cmi_predict(betas_hm450, cmi_model)
```

```{r}
sessionInfo()
```
